Analysis for Victor Court

### 2018-07-10 Articles/Court_Analysis_2018/FittingForCourt2018.Rmd
Working on Victor Court paper.

```{r}
kleModel <- cesModel(y ~ k + l + e, data = USData)
kleModel
nckle <- naturalCoef(kleModel)
nckle
```

Note that $\delta = 1$, so this is a boundary model.
We also have $\rho_1 = -1$ (therefore, $\sigma_1 = \infty$). 
We can query which boundary model we have: 
```{r}
kleModel$bname
```
So this is boundary model 7 of Table 2 in the ``Cautionary Tales'' paper.

@@

$$y = `r exp(coef(kleModel)[["logscale"]])` 
      \mathrm{e}^{-`r coef(kleModel)[["lambda"]]` (t-1960)} 
      \left[ `r coef(kleModel)[["delta_1"]]` \, k 
          + `r 1 - coef(kleModel)[["delta_1"]]` \, l \right] \; .$$

@@

1. The fit is rather good.
2. It is likely that the fitted model excludes energy ($e$), 
   because the energy dip in 1980 is too large. 
   Instead, by picking up the smaller dip in the $l$ data series, the fit is better.
3. I find it interesting, but don't quite know what to make of it, that
   the coefficients on $k$ and $l$ are approximately the neoclassical numbers 
   (0.7 and 0.3, respectively).

>>>>

```{r}
kleModel <- cesModel(y ~ k + l + e, data = USData)
kleModel
```
Note that $\delta = 1$, so this is a boundary model.
We also have $\rho_1 = -1$ (therefore, $\sigma_1 = \infty$).

We can query which boundary model we have: 
```{r}
kleModel$bname
```
So this is boundary model 7 of Table 2 in the ``Cautionary Tales'' paper.

We can see the ``natural'' coefficients for the model.
```{r}
nckle <- naturalCoef(kleModel)
nckle
```

@@

$$y = `r exp(coef(kleModel)[["logscale"]])` 
      \mathrm{e}^{`r coef(kleModel)[["lambda"]]` (t-1960)} 
      \left[ `r coef(kleModel)[["delta_1"]]` \, k 
          + `r 1 - coef(kleModel)[["delta_1"]]` \, l \right] \; .$$

@@

1. The fit is rather good.
2. It is likely that the fitted model excludes energy ($e$), 
   because the energy dip in 1980 puts the energy trajectory at a very different
   multiple of the $y$ curve. 
   In contrast, the $l$ curve stays at about the same multiple of $y$
   throughout the entire time series. 
   Thus, the $l$ curve . 
   Instead, by picking up the smaller dip in the $l$ data series, the fit is better.
3. I find it interesting, but don't quite know what to make of it, that
   the coefficients on $k$ and $l$ are approximately the neoclassical numbers 
   (0.7 and 0.3, respectively).
